### 2016-06-01 TreeLevel.tex
push before restructering: move Subprocesses to Partonic Cross Sections

Fig. ... shows a parton density function set for the proton. One can see that the partons most probable to carry a high fraction of momentum are the valence quarks. For lower values of $x$ gluons constitute the major component of the proton.\\

@@

@@

\subsubsection*{The process $GG \to \tilde{q}\tilde{q}^\dagger$}
This process has the same cross section in the MRSSM and in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in {L,R}$ can be produced

@@

When considering squark production one has to sum over all $|\mathcal{M}|^2$ with different helicity. The diagrams for those different final state helicities are shown for flavor like squark production in tab. \ref{tab:squark_likeflavor} and for flavor unlike squark production in tab. \ref{tab:squark_unlikeflavor} for the MSSM and the MRSSM. To avoid double counting one needs to weight $|\mathcal{M}|^2(qq\to \tilde{q}_L\tilde{q}_L)$ and $|\mathcal{M}|^2(qq\to \tilde{q}_R\tilde{q}_R)$ with a statistical factor of $\frac{1}{2}$ as one integrates over all momenta of both particles to arrive at the cross section.\footnote{Alternatively one could discard the $u$-channel (or $t$-channel) diagram and omit the weighting with $\frac{1}{2}$.}

@@

	\node at (2.2,0) {$\tilde{u}_R^\dagger$};

@@

	\node at (2.2,0) {$\tilde{u}_L^\dagger$};

@@

	\node at (2.2,1) {$\tilde{u}_R^\dagger$};
	\node at (2.2,0) {$\tilde{u}_R^\dagger$};

@@

@@

	\node at (2.2,1) {$\tilde{u}_R^\dagger$};
	\node at (2.2,0) {$\tilde{d}_L^\dagger$};

@@

	\node at (2.2,0) {$\tilde{d}_L^\dagger$};

@@

	\node at (2.2,1) {$\tilde{u}_R^\dagger$};

@@

Because of the absence of chirality like squarks in the final state in the MRSSM (and a missing interference of the two diagrams in tab. \ref{tab:squark_likeflavor} in the MRSSM) the cross section of flavor like and unlike squarks is the same in the MRSSM, i.e. on the partonic level:\\ $\sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(\tilde{u}_L\tilde{u}_R) = \sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(\tilde{u}_L\tilde{d}_R)$. That is however not true in the MSSM.

\subsubsection*{The process $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$}
In contrast to the MSSM no statistical factor of $\frac{1}{2}$ is taken into account when turning from $|\mathcal{M}|^2$ to $\sigma$. This is because gluino and antigluino are distinguishable particles. Still in comparison to the MSSM cross section only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines origin from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities. Furthermore an interference term from the $t$ or $u$ channel diagram which occurs in the MSSM is absent in the MRSSM.
% this interference term causes a huge difference, that's been checked by Philip via Madgraph

@@

\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row). In the final state it has been summed over all squark flavors expect for staus. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton densities and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}.}\label{fig:TreeLevelSigma_0,9_2}
\end{center}
\end{figure}

\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.4]{figures/mr=5_MSSM+MRSSM}
\includegraphics[scale=.45]{figures/rel_weights_mr=5_MSSM+MRSSM}
\caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to 5. In the final state it has been summed over all squark flavors expect for staus. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton densities and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}.}
\end{center}
\end{figure}

@@

\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MSSM+MRSSM_msg=2000}
\includegraphics[scale=.5]{figures/MSSM+MRSSM_msq=1000}
\caption{add error bars}
\end{center}
\end{figure}

>>>>

\includegraphics[scale=0.6]{figures/pdf's}
\caption{pdf's}\label{fig:pdfs}
Fig. \ref{fig:pdfs} shows a parton density function set for the proton. One can see that the partons most probable to carry a high fraction of momentum are the valence quarks. For lower values of $x$ gluons constitute the major component of the proton.\\

@@

\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row). In the final state it has been summed over all squark flavors expect for staus. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton densities and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}.}\label{fig:TreeLevelSigma_0,9_2}

@@

\subsubsection*{The process $GG \to \tilde{q}\tilde{q}^\dagger$}
This process has the same cross section in the MRSSM and in the MSSM for also in the MSSM only like chirality squark and antisquark $\tilde{q}_A\tilde{q}_A^\dagger$ with $A \in {L,R}$ can be produced.

@@

When considering squark production one has to sum over all $|\mathcal{M}|^2$ with different helicity. The diagrams for those different final state helicities are shown for flavor like squark production in tab. \ref{tab:squark_likeflavor} and for flavor unlike squark production in tab. \ref{tab:squark_unlikeflavor} for the MSSM and the MRSSM. To avoid double counting one needs to weight $|\mathcal{M}|^2(qq\to \tilde{q}_L\tilde{q}_L)$ and $|\mathcal{M}|^2(qq\to \tilde{q}_R\tilde{q}_R)$ with a statistical factor of $\frac{1}{2}$ as one integrates over all momenta of both particles to arrive at the cross section.

@@

	\node at (2.5,1) {$\tilde{u}_L^\dagger$};
	\node at (2.5,0) {$\tilde{u}_R^\dagger$};

@@

	\node at (2.5,1) {$\tilde{u}_L^\dagger$};
	\node at (2.5,0) {$\tilde{u}_L^\dagger$};

@@

	\node at (2.5,1) {$\tilde{u}_R^\dagger$};
	\node at (2.5,0) {$\tilde{u}_R^\dagger$};

@@

	\node at (2.5,1) {$\tilde{u}_L^\dagger$};
	\node at (2.5,0) {$\tilde{d}_R^\dagger$};

@@

	\node at (2.5,1) {$\tilde{u}_R^\dagger$};
	\node at (2.5,0) {$\tilde{d}_L^\dagger$};

@@

	\node at (2.5,1) {$\tilde{u}_L^\dagger$};
	\node at (2.5,0) {$\tilde{d}_L^\dagger$};

@@

	\node at (2.5,1) {$\tilde{u}_R^\dagger$};
	\node at (2.5,0) {$\tilde{d}_R^\dagger$};

@@

Because of the absence of chirality like squarks in the final state in the MRSSM (and a missing interference of the two diagrams in tab. \ref{tab:squark_likeflavor} in the column of the MRSSM) the partonic cross section of flavor like and unlike squarks is the same in the MRSSM, i.e. on the partonic level:
\sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(uu \to \tilde{u}_L\tilde{u}_R) = \sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(ud \to \tilde{u}_L\tilde{d}_R) + \sigma^{\mathrm{B}}_{\mathrm{Part,\ MRSSM}}(ud \to \tilde{u}_R\tilde{d}_L).
That is however not true in the MSSM because for flavor like squarks there is a non vanishing interference of the $t$- and $u$-channel diagram of the processes $qq \to \tilde{q}_L\tilde{q}_L$ and $qq \to \tilde{q}_R\tilde{q}_R$. This term is given in \cite[p.7]{Beenakker:1996ch}\\
Looking at the hadronic cross section in fig. \ref{fig:TreeXsection} can see the suppression of squark production in the MRSSM in comparison to the MSSM. One can also see that this suppression grows when going from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ or even to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ in fig. \ref{fig:TreeXsection5}. This reflects the gluino mass dependence explained above. See also \ref{fig:TreeXsection_fixed_m} for a visualization of this behavior.\\
Note also that for sufficiently large squark masses squark production is the dominant process, see fig. \ref{fig:TreeXsection} and \ref{fig:TreeLevelSigma_0,9_2}. This is because the production of heavy particles requires large longitudinal momenta of the colliding partons, i.e. large $x$. Looking at the parton density functions in fig. \ref{fig:pdfs} one sees that within the proton the partons most likely to carry large momentum are quarks. So looking at large $x$ the proton basically consists of quarks and because the only process involving only quarks in the initial state is squark production, this channel dominates for high masses.

\subsubsection*{The process $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$}
In contrast to the MSSM no statistical factor of $\frac{1}{2}$ is taken into account when turning from $|\mathcal{M}|^2$ to $\sigma$. This is because gluino and antigluino are distinguishable particles. Still in comparison to the MSSM cross section \cite[p.9]{Beenakker:1996ch} only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the other two lines originate from an $t$ or $u$ channel squark which occurs in only one instead of two chiralities. Furthermore an interference term from the $t$ or $u$ channel diagram which occurs in the MSSM is absent in the MRSSM. For a growing gluino mass it is this interference term which makes the cross section in the MRSSM dominant over the one in the MSSM.
% this interference term causes a huge difference, that's been checked by Philip via Madgraph

@@

\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.4]{figures/mr=5_MSSM+MRSSM}
\includegraphics[scale=.45]{figures/rel_weights_mr=5_MSSM+MRSSM}
\caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to 5. In the final state it has been summed over all squark flavors expect for staus. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton densities and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}.}\label{fig:TreeXsection5}
\end{center}
\end{figure}

@@

\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MSSM+MRSSM_msg=2000}
\includegraphics[scale=.5]{figures/MSSM+MRSSM_msq=1000}
\caption{add error bars}\ref{fig:TreeXsection_fixed_m}
\end{center}
\end{figure}
